\noindent\textbf{Mass}: pleural mass, mediastinal mass, mass, breast mass, pulmonary mass, soft tissue mass.

\noindent\textbf{Lung}: chronic changes, calcified granuloma, granuloma, nodule, multiple nodules, cyst, cavitation, fibrotic band, volume loss, hypoexpansion, hypoexpansion basal, bullas, lung vascular paucity, air trapping, bronchiectasis, infiltrates, interstitial pattern, ground glass pattern, reticular interstitial pattern, reticulonodular interstitial pattern, miliary opacities, alveolar pattern, consolidation, air bronchogram, bronchovascular markings, increased density, atelectasis, total atelectasis, lobar atelectasis, segmental atelectasis, laminar atelectasis, round atelectasis, atelectasis basal, azygos lobe, vascular redistribution, central vascular redistribution, kerley lines, pneumonia, atypical pneumonia, tuberculosis, tuberculosis sequelae, lung metastasis, pulmonary fibrosis, post radiotherapy changes, asbestosis signs, emphysema, COPD signs, heart insufficiency, respiratory distress, pulmonary hypertension, pulmonary artery hypertension, pulmonary venous hypertension, pulmonary edema, bone metastasis, pulmonary mass.

\noindent\textbf{Lung-urgent}: nodule, multiple nodules, infiltrates, interstitial pattern, ground glass pattern, reticular interstitial pattern, reticulonodular interstitial pattern, miliary opacities, alveolar pattern, consolidation, air bronchogram, atelectasis, total atelectasis, lobar atelectasis, segmental atelectasis, laminar atelectasis, round atelectasis, atelectasis basal, pneumonia, atypical pneumonia, pulmonary mass.

\noindent\textbf{Nodules / Multiple nodules}: nodule, multiple nodules.

\noindent\textbf{Pneumonia}: pneumonia, atypical pneumonia.

\noindent\textbf{Infiltrates}: infiltrates, interstitial pattern, ground glass pattern, reticular interstitial pattern, reticulonodular interstitial pattern, miliary opacities, alveolar pattern, consolidation, air bronchogram.

\noindent\textbf{Atelectasis}: atelectasis, total atelectasis, lobar atelectasis, segmental atelectasis, laminar atelectasis, round atelectasis, atelectasis basal.

\noindent\textbf{COPD / Emphysema}: emphysema, COPD signs.

\noindent\textbf{MH}: calcified adenopathy, calcified mediastinal adenopathy, heart valve calcified, pneumomediastinum, mediastinal shift, hilar enlargement, adenopathy, vascular hilar enlargement, pulmonary artery enlargement, hilar congestion, cardiomegaly, dextrocardia, right sided aortic arch, aortic atheromatosis, aortic elongation, descendent aortic elongation, ascendent aortic elongation, aortic button enlargement, supra aortic elongation, aortic aneurysm, mediastinal enlargement, superior mediastinal enlargement, goiter, mediastinal mass, tracheal shift, esophagic dilatation, azygoesophageal recess shift, mediastinic lipomatosis.

\noindent\textbf{MH-urgent}: hilar enlargement, adenopathy, hilar congestion, cardiomegaly, superior mediastinal enlargement, mediastinal mass, tracheal shift.

\noindent\textbf{Cardiomegaly}: cardiomegaly.

\noindent\textbf{Hila}: hilar enlargement, adenopathy, hilar congestion.

\noindent\textbf{Vascular hilar enlargement}: vascular hilar enlargement, pulmonary artery enlargement.

\noindent\textbf{Aortic elongation}: aortic elongation, descendent aortic elongation, ascendent aortic elongation, aortic button enlargement, supra aortic elongation.

\noindent\textbf{PDTW}: calcified pleural plaques, calcified pleural thickening, pneumothorax, hydropneumothorax, pneumoperitoneo, subcutaneous emphysema, flattened diaphragm, fissure thickening, minor fissure thickening, major fissure thickening, loculated fissural effusion, pleural thickening, apical pleural thickening, pleural plaques, pleural effusion, loculated pleural effusion, pericardial effusion, hiatal hernia, pleural mass, costophrenic angle blunting, thoracic cage deformation, scoliosis, kyphosis, pectum excavatum, pectum carinatum, cervical rib, vertebral degenerative changes, lytic bone lesion, sclerotic bone lesion, blastic bone lesion, costochondral junction hypertrophy, sternoclavicular junction hypertrophy, axial hyperostosis, osteopenia, osteoporosis, non axial articular degenerative changes, subacromial space narrowing, fracture, clavicle fracture, humeral fracture, vertebral fracture, rib fracture, callus rib fracture, gynecomastia, Chilaiditi sign, hemidiaphragm elevation, diaphragmatic eventration, soft tissue mass.

\noindent\textbf{PDTW-urgent}: pneumothorax, hydropneumothorax, subcutaneous emphysema, loculated fissural effusion, pleural effusion, loculated pleural effusion, pleural mass, costophrenic angle blunting, lytic bone lesion, sclerotic bone lesion, blastic bone lesion, fracture, clavicle fracture, humeral fracture, vertebral fracture, rib fracture, soft tissue mass.

\noindent\textbf{Pleural effusion}: hydropneumothorax, loculated fissural effusion, pleural effusion, loculated pleural effusion.

\noindent\textbf{Pneumothorax}: pneumothorax, hydropneumothorax.

\noindent\textbf{Costophrenic angle blunting}: costophrenic angle blunting.

\noindent\textbf{PDTW-incidental}: calcified pleural thickening, pleural thickening, apical pleural thickening, vertebral degenerative changes, non axial articular degenerative changes, callus rib fracture.

\noindent\textbf{Vertebral degenerative changes}: vertebral degenerative changes.

\noindent\textbf{Hiatal hernia}: hiatal hernia.

\noindent\textbf{Foreign bodies}: tracheostomy tube, endotracheal tube, NSG tube, chest drain tube, ventriculoperitoneal drain tube, catheter, central venous catheter, central venous catheter via subclavian vein, central venous catheter via jugular vein, reservoir central venous catheter, central venous catheter via umbilical vein, electrical device, dual chamber device, single chamber device, pacemaker, dai, artificial heart valve, artificial mitral heart valve, artificial aortic heart valve, surgery, metal, osteosynthesis material, sternotomy, suture material, bone cement, prosthesis, humeral prosthesis, mammary prosthesis, endoprosthesis, aortic endoprosthesis, surgery breast, mastectomy, surgery neck, surgery lung, surgery heart, surgery humeral.

\noindent\textbf{Electrical devices}: electrical device, dual chamber device, single chamber device, pacemaker, dai.

\noindent\textbf{Tube}: tracheostomy tube, endotracheal tube, NSG tube, chest drain tube, ventriculoperitoneal drain tube.

\noindent\textbf{NSG Tube}: NSG tube.

\noindent\textbf{Catheter}: catheter, central venous catheter, central venous catheter via subclavian vein, central venous catheter via jugular vein, reservoir central venous catheter, central venous catheter via umbilical vein.

\noindent\textbf{Surgery}: surgery, metal, osteosynthesis material, sternotomy, suture material, bone cement, prosthesis, humeral prosthesis, mammary prosthesis, endoprosthesis, aortic endoprosthesis, surgery breast, mastectomy, surgery neck, surgery lung, surgery heart, surgery humeral.

\noindent\textbf{Calcification}: calcified densities, calcified granuloma, calcified adenopathy, calcified mediastinal adenopathy, calcified pleural plaques, heart valve calcified, calcified fibroadenoma, calcified pleural thickening, pleural plaques, aortic atheromatosis.

\noindent\textbf{Pseudonodule}: pseudonodule, nipple shadow, end on vessel.

\noindent\textbf{Suboptimal}: suboptimal study.

